Constraint Programming - Inside Gecode

### 2014-05-05 paper.tex
removed C++-code and pseudo code

	\section{Introduction}
	Constraint programming is a tool to solve mathematical problems through the formulation of constraints, which describe the desired solution. As usually a formal and exact definition, like it can be found in \cite[p.~16]{handbookCP} for constraint programming, is not as helpful as an example, I would like to give you a short overview on the topic through the well known problem \emph{SEND MORE MONEY}.

>>>>

	\section{Introduction}
	Constraint programming is a method to solve mathematical problems through the formulation of constraints, which describe the desired solution. As a formal and exact definition, like it can be found in \cite[p.~16]{handbookCP} for constraint programming, is not as helpful as an example, I would like to give you a short overview on the topic through the well known problem \emph{SEND MORE MONEY}.
